MapReduce to My Ears\\ {\Large Using Big Data for Music Synthesis}

### 2013-05-10 writeup/paper.tex
Added abstract

\begin{abstract}
\end{abstract}

>>>>

\begin{abstract}
Every young computer scientist learns early in their career that all data regardless of its meaning are all the same in their underlying representation - simple ones and zeroes.
It is only in the act of reading and subsequently interpreting those data that computer scientists or their creations give meaning to the bits and bytes.
MapReduce to My Ears is an exercise in the reinterpretation of data meant to be understood as color and picture into sound and music.
Our method uses Hadoop, an open source implementation of the MapReduce programming paradigm, to process a large corpus of images and extract a musical representation.
We have produce a six minutes and thirty-five second audio/visual entitled \emph{Digital Nightmare}, the style of which can be described as 8-bit, blast beat.
\end{abstract}
